---
title: GICS
output: github_document
---

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)


<style> body {text-align: justify} </style>

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
library(GICS)

knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.path = "README-")
data(list = c("standards"), package = "GICS")
```

  
  
## GICS  

GICS packages the Global Industry Classification Standard (GICS) dataset for consumption in R. Install the development version from [github](https://github.com/bautheac/GICS/) using: `devtools::install_github("bautheac/GICS")`.  
The GICS is a standardized classification system for equities developed jointly by Morgan Stanley Capital International (MSCI) and Standard & Poor's. The GICS methodology is used by the MSCI indexes, which include domestic and international stocks, as well as by a large portion of the professional investment management community. The GICS hierarchy begins with 11 sectors and is followed by 24 industry groups, 68 industries, and 157 sub-industries. Each stock that is classified will have a coding at all four of these levels.

Excerpt of the 'standards' dataset:
```{r `countries`, echo = FALSE}
head(standards)
```


### finRes

Although GICS is self-contained with consumption value on its own, it belongs to [finRes](https://bautheac.github.io/finRes/) where it helps with data wrangling and analysis.



